# functions

## setParams()

`setParams()` generates a `Params` object of class specified by the `method` argument, i.e. `method = "Seurat"` returns a `SeuratParams` object. The slots of the object can be modified on calling `setParams()` by passing in the name of the slot and the value into the function. i.e `batch = "batch"` 

```{r eval=FALSE}
setParams(method = "Seurat", ...)
```

**Arguments**

| Argument | Description |
| --- | --- |
| **method** | character vector specifying the integration method, currently the following methods are available `c("Seurat", "Harmony", "Liger", "Scanorama", "BBKNN")` |
| **...** | additional arguments that modify the slots of the `Params` object specified by the `methods` argument |

## Merge()

`Merge()` generates a `SingleCellExperiment` object that has been batch integrated by the method specified in the `params` object. 

```{r eval=FALSE}
Merge(params, data)
```

**Arguments**

| Argument | Description |
| --- | --- |
| **params** | A `params` object generated by the `setParams` function |
| **data** | A `SummarizedExperiment` or `SingleCellExperiment` object with a metadata identifying the batches |